### 2021-12-08 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@0df28077f8bcc3a3e5912907b85311d7e7d64ee0 🚀

summary of model challenges for networks

@@

@@

@@

\hypertarget{references}{%
\section{References}\label{references}}

>>>>

summary of model challenges for networks - Strydom et al. (2021)
importance of drawing on traits + validation is challenging - Whalen et
al. (2021) machine learning from genomics

@@

\hypertarget{confusion-matrix-with-skill-and-bias}{%
\subsection{Confusion matrix with skill and
bias}\label{confusion-matrix-with-skill-and-bias}}

@@

\hypertarget{what-are-the-baseline-values-of-performance-measures}{%
\subsection{What are the baseline values of performance
measures?}\label{what-are-the-baseline-values-of-performance-measures}}

In this section, we will change the values of \(b\) abd \(s\) for a
given value of \(\rho\), and see how the values of common performance
measures for binary classification are affected.

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
Strydom, T., Catchen, M. D., Banville, F., Caron, D., Dansereau, G.,
Desjardins-Proulx, P., Forero-Muñoz, N. R., Higino, G., Mercier, B.,
Gonzalez, A., Gravel, D., Pollock, L., \& Poisot, T. (2021). A roadmap
towards predicting species interaction networks (across space and time).
\emph{Philosophical Transactions of the Royal Society B: Biological
Sciences}, \emph{376}(1837), 20210063.
\url{https://doi.org/10.1098/rstb.2021.0063}

\leavevmode\hypertarget{ref-Whalen2021NavPit}{}%
Whalen, S., Schreiber, J., Noble, W. S., \& Pollard, K. S. (2021).
Navigating the pitfalls of applying machine learning in genomics.
\emph{Nature Reviews Genetics}, 1--13.
\url{https://doi.org/10.1038/s41576-021-00434-9}

\end{CSLReferences}
